Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-05-20 paper_aracna/main.tex
Finished cleaning up figures and references.

\documentclass[letterpaper]{article}
\usepackage{natbib,alife13}

@@

\begin{figure}[t]
\begin{center}
%\includegraphics[width=.45\textwidth]{fig1.jpg}
\includegraphics[width=\columnwidth]{fig1.jpg}
\caption{Aracna: an open-sourced quadruped robot platform. All
  instructions and downloads are publicly available at
  http://creativemachines.cornell.edu/aracna .}
\label{fig1}
\end{center}
\end{figure}

@@

In this paper we address these needs by introducing \emph{Aracna}, a low-cost, open-source hardware, easily customizable robot platform with non-intuitive walking
kinematics~(Figure 1). Aracna is the third quadruped robot developed for evolutionary learning algorithms by the Creative Machines Lab at Cornell University~\citep{bongard2006resilient, yosinski2011gaits}. Like the most recent of the two previous designs, called QuadraTot~\citep{yosinski2011gaits}, the body of Aracna is 3D printed and the STL files are available online,
%TODO: INSERT LINK
meaning that other researchers can easily customize the body's design. As in the both previous designs, each leg has a hip and knee joint controlled by two actuators. The original Creative
Machines Lab quadruped robot favored starfish-like movements~\citep{bongard2006resilient}. The second quadruped robot --- QuadraTot ---
developed spider-like movements, but was found to be limited by its
weight, such that the motors would overheat and timeout when trying to execute many commands~\citep{yosinski2011gaits, Glette2012Evolution}. We designed Aracna to be able to produce fast, spider-like movements, yet be lightweight enough that the motors would not overheat. We also designed Aracna to be inexpensive: as described below, its overall price is under \$1,400  USD. In the following sections we describe the Aracna platform in more detail.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{fig5.jpg}
\caption{A rendered CAD model of Aracna. Note the lack of heavy servos on the legs themselves, which are instead controlled via four-bar linkages by servos in the robot's core.}
\label{cadModelOfRobot}
\end{center}
\end{figure}

@@

The hardware of Aracna was designed to improve upon the previous Creative Machines Lab
quadruped robots~\citep{bongard2006resilient, yosinski2011gaits}, while still qualitatively resembling those robots. Aracna is similar in that it has a body and four legs, with each leg having two joints that can pitch forward and back like knees~(Figure~\ref{cadModelOfRobot}).

@@

A major modification, targeted at reducing the weight of legs, was the use of two four-bar mechanisms to drive the joints in each
leg. This mechanism causes the controlled joint to move at a fraction
of the output angle of the actuator, giving the motor a relatively
larger mechanical advantage over the position of each leg.
Figure~\ref{crankRocker} shows the crank-rocker system, where the input crank
is actuated by a servo and the rocker is the leg. This
configuration allows the servo motors to be contained in the robot core, reducing both the inertia and mass of each leg. The weight of an Aracna leg is 105g compared to the 217g for a QuadraTot leg.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.23\textwidth]{fig3.pdf}
\includegraphics[width=.23\textwidth]{fig4.pdf}
\caption{Crank-rocker four-bar linkage controlling flexion/extension of
  the knee and hip joints. In both cases above, the input crank (link
  OA) is actuated by a servo, the rocker is the leg (link CB), and the
  fixed link is OC.}
\label{crankRocker}
\end{center}
\end{figure}

@@

An initial version of Aracna was designed to be printed in one piece~(Figure~\ref{notYetCleanedOnePieceRobot}). However, if one part of the robot became damaged, an entire new robot had to be reprinted, which took over 26 hours and costs roughly \$355 USD on an Objet Connex500 printer. To make repairing the robot easier, cheaper, and quicker, Aracna was redesigned to be modular. It consists of 15 pieces--four legs and the core--that can be separately 3D printed~(Figure~\ref{notYetCleanedMulitPieceRobot}). Printing a leg takes 3.3 hours and costs roughly \$64 USD. Printing the core takes 3 hours and costs \$101 USD. All 15 Aracna pieces can still be printed as one print job, with an overall time of approximately 10 hours and cost of \$308. These figures are based on Aracna's use of  approximately 967g of model material and 746g of support material, and current material costs of 4.5g per USD and 8g per USD for rigid and support material, respectively. This cost estimate is variable depending on the type of material used. The print times are estimates calculated by the Objet's software and are meant to be used as a relative comparison of print times. Table~\ref{tab:cost} outlines the total estimated cost of Aracna, which is just under \$1,400, including its off-the-shelf electronic components.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.37\textwidth]{fig2.jpg}
\caption{A draft version of Aracna that was printed in one piece. This non-modular design proved expensive to maintain if part of the robot was damaged, and was replaced in a later version with a modular design. This image is of the printed body with support material still present.}
\label{notYetCleanedOnePieceRobot}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.37\textwidth]{fig6.jpg}
\caption{A final version of Aracna printed in multiple pieces.The body is printed as two pieces, with 9 smaller parts within the top piece to reduce support material and print time. These parts can be printed individually if replacements are necessary. The body consists of a total of 11 parts. This image shows a set of 12 printed parts (the complete body and a single leg) with support material still present.}
\label{notYetCleanedMulitPieceRobot}
\end{center}
\end{figure}

\begin{table}[h]
\center{
\begin{tabular}{|c|c|}
\hline
Part & Cost\\
\hline\hline
3D Print Materials & \$308\\
ArbotiX Robocontroller Kit & \$189\\
Dynamixel AX-18A Robot Actuator (x8) & \$721\\
3S 11.1V 2000mAh Pro Lite LiPo Battery & \$73\\
LiPo Battery Balance Charger Kit & \$70\\
Cables, Connectors, Misc & \$28\\
\hline\hline
\bf Total & \bf \$1389\\
 \hline
\end{tabular}
}
\vskip 0.25cm
\caption{Estimated total cost. The cost of components and printing material reflect market prices from March 2012. A complete parts list is on our website \citep{WEB}.}
\label{tab:cost}
\end{table}

>>>>

\documentclass[letterpaper]{article}
\usepackage{natbib,alife13}
\usepackage{ownstyles}

\graphicspath{{../figures/}}

@@

%\begin{figure}[t]
%\begin{center}
%%\includegraphics[width=.45\textwidth]{aracna_black_1.jpg}
%\includegraphics[width=\columnwidth]{aracna_black_1.jpg}
%\caption{Aracna: an open-sourced quadruped robot platform. All
%  instructions and downloads are publicly available at
%  http://creativemachines.cornell.edu/aracna .}
%\label{fig:aracna_black_1}
%\end{center}
%\end{figure}

\figp{aracna_black_1}{1}{Aracna: an open-sourced quadruped robot
  platform. All instructions and downloads are publicly available at
  http://creativemachines.cornell.edu/aracna.}{}

@@

In this paper we address these needs by introducing \emph{Aracna}, a low-cost, open-source hardware, easily customizable robot platform with non-intuitive walking
kinematics~(\figref{aracna_black_1}). Aracna is the third quadruped robot developed for evolutionary learning algorithms by the Creative Machines Lab at Cornell University~\citep{bongard2006resilient, yosinski2011gaits}. Like the most recent of the two previous designs, called QuadraTot~\citep{yosinski2011gaits}, the body of Aracna is 3D printed and the STL files are available online,
%TODO: INSERT LINK
meaning that other researchers can easily customize the body's design. As in the both previous designs, each leg has a hip and knee joint controlled by two actuators. The original Creative
Machines Lab quadruped robot favored starfish-like movements~\citep{bongard2006resilient}. The second quadruped robot --- QuadraTot ---
developed spider-like movements, but was found to be limited by its
weight, such that the motors would overheat and timeout when trying to execute many commands~\citep{yosinski2011gaits, Glette2012Evolution}. We designed Aracna to be able to produce fast, spider-like movements, yet be lightweight enough that the motors would not overheat. We also designed Aracna to be inexpensive: as described below, its overall price is under \$1,400  USD. In the following sections we describe the Aracna platform in more detail.

@@

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=\columnwidth]{aracna_cad_ver1.jpg}
%\caption{A rendered CAD model of Aracna. Note the lack of heavy servos on the legs themselves, which are instead controlled via four-bar linkages by servos in the robot's core.}
%\label{fig:aracna_cad_ver1.jpg}
%\end{center}
%\end{figure}

\figp{aracna_cad_ver1}{1}{A rendered CAD model of Aracna. Note the
  lack of heavy servos on the legs themselves, which are instead
  controlled via four-bar linkages by servos in the robot's core.}

@@

The hardware of Aracna was designed to improve upon the previous Creative Machines Lab
quadruped robots~\citep{bongard2006resilient, yosinski2011gaits}, while still qualitatively resembling those robots. Aracna is similar in that it has a body and four legs, with each leg having two joints that can pitch forward and back like knees~(\figref{aracna_cad_ver1}).

@@

A major modification, targeted at reducing the weight of legs, was the use of two four-bar mechanisms to drive the joints in each
leg. This mechanism causes the controlled joint to move at a fraction
of the output angle of the actuator, giving the motor a relatively
larger mechanical advantage over the position of each leg.
\figref{aracna_leg_drawing_outer} shows the crank-rocker system, where the input crank
is actuated by a servo and the rocker is the leg. This
configuration allows the servo motors to be contained in the robot core, reducing both the inertia and mass of each leg. The weight of an Aracna leg is 105g compared to the 217g for a QuadraTot leg.

@@

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=.23\textwidth]{aracna_leg_drawing_outer}
%\includegraphics[width=.23\textwidth]{aracna_leg_drawing_inner}
%\caption{Crank-rocker four-bar linkage controlling flexion/extension of
%  the knee and hip joints. In both cases above, the input crank (link
%  OA) is actuated by a servo, the rocker is the leg (link CB), and the
%  fixed link is OC.}
%\label{fig:crankRocker}
%\end{center}
%\end{figure}

\figgp{aracna_leg_drawing_outer}{.46}{aracna_leg_drawing_inner}{.46}{Crank-rocker
  four-bar linkage controlling flexion/extension of the knee and hip
  joints. In both cases above, the input crank (link OA) is actuated
  by a servo, the rocker is the leg (link CB), and the fixed link is
  OC.}

@@

An initial version of Aracna was designed to be printed in one piece~(\figref{aracna_notYetCleanedOnePieceRobot}). However, if one part of the robot became damaged, an entire new robot had to be reprinted, which took over 26 hours and costs roughly \$355 USD on an Objet Connex500 printer. To make repairing the robot easier, cheaper, and quicker, Aracna was redesigned to be modular. It consists of 15 pieces--four legs and the core--that can be separately 3D printed~(\figref{aracna_notYetCleanedMultiPieceRobot}). Printing a leg takes 3.3 hours and costs roughly \$64 USD. Printing the core takes 3 hours and costs \$101 USD. All 15 Aracna pieces can still be printed as one print job, with an overall time of approximately 10 hours and cost of \$308. These figures are based on Aracna's use of  approximately 967g of model material and 746g of support material, and current material costs of 4.5g per USD and 8g per USD for rigid and support material, respectively. This cost estimate is variable depending on the type of material used. The print times are estimates calculated by the Objet's software and are meant to be used as a relative comparison of print times. Table~\ref{tab:cost} outlines the total estimated cost of Aracna, which is just under \$1,400, including its off-the-shelf electronic components.

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=.37\textwidth]{aracna_notYetCleanedOnePieceRobot.jpg}
%\caption{A draft version of Aracna that was printed in one piece. This non-modular design proved expensive to maintain if part of the robot was damaged, and was replaced in a later version with a modular design. This image is of the printed body with support material still present.}
%\label{fig:aracna_notYetCleanedOnePieceRobot}
%\end{center}
%\end{figure}

\figp{aracna_notYetCleanedOnePieceRobot}{.74}{A draft version of
  Aracna that was printed in one piece. This non-modular design proved
  expensive to maintain if part of the robot was damaged, and was
  replaced in a later version with a modular design. This image is of
  the printed body with support material still present.}

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=.37\textwidth]{aracna_notYetCleanedMultiPieceRobot.jpg}
%\caption{A final version of Aracna printed in multiple pieces.The body is printed as two pieces, with 9 smaller parts within the top piece to reduce support material and print time. These parts can be printed individually if replacements are necessary. The body consists of a total of 11 parts. This image shows a set of 12 printed parts (the complete body and a single leg) with support material still present.}
%\label{fig:aracna_notYetCleanedMultiPieceRobot}
%\end{center}
%\end{figure}

\figp{aracna_notYetCleanedMultiPieceRobot}{.74}{A final version of
  Aracna printed in multiple pieces.The body is printed as two pieces,
  with 9 smaller parts within the top piece to reduce support material
  and print time. These parts can be printed individually if
  replacements are necessary. The body consists of a total of 11
  parts. This image shows a set of 12 printed parts (the complete body
  and a single leg) with support material still present.}

\begin{table}[h]
\center{
\begin{tabular}{|c|c|}
\hline
Part & Cost\\
\hline\hline
3D Print Materials & \$308\\
ArbotiX Robocontroller Kit & \$189\\
Dynamixel AX-18A Robot Actuator (x8) & \$721\\
3S 11.1V 2000mAh Pro Lite LiPo Battery & \$73\\
LiPo Battery Balance Charger Kit & \$70\\
Cables, Connectors, Misc & \$28\\
\hline\hline
\bf Total & \bf \$1389\\
 \hline
\end{tabular}
}
\vskip 0.25cm
\caption{Estimated total cost. The cost of components and printing material reflect market prices from March 2012. A complete parts list is on our website \citep{WEB}.}
\tablabel{cost}
\end{table}
